Irt plot extra

### 2022-03-27 manuscript.Rmd
minimum-maximum factor loading corrected

-   Supplementary Table S1 Overview Existing Related Scales: items in total / items on light exposure (behaviour)

@@

# loading
min.loadings <- abs(min(Fac.5$loadings))
max.loadings <- abs(max(Fac.5$loadings))

>>>>

-   Supplementary Table S1: Overview Existing Related Scales

@@

# loading
Fac.5.min.max <- Fac.5$loadings %>% 
  subset(abs(Fac.5$loadings)>(.3))
min.loadings <- min(abs(Fac.5.min.max))
max.loadings <- max(Fac.5.min.max)
